\section*{Contributions of the Team}
\label{sec:contributions}

\paragraph{Amangeet Samra}
She helped code the FastAPI implementation of user (with Catherine) and source app applications. She wrote Section \ref{sec:discussion} section of the paper (with Mahesh). She put-together the slide-deck for the project presentation. She edited the final paper for grammar, correctness and style.

\paragraph{Amrita Mande}
She worked on the writeup for Section \ref{sec:method} (with Mahesh). She contributed to the overall architecture of \name and the high-level design of the proof-of-concept implementation. She identified various scenarios to break/attack the system. 

\paragraph{Catherine Jimerson}
She helped code the FastAPI implementation of user application (with Geet). She worked on the writeup for Sections \ref{sec:intro} (with Diamond) and \ref{sec:results}. She contributed to the animation of the slide-deck and fine-tuned the intuitive explanation of the methods. 

\paragraph{Diamond Rorie}
She did the research/reading for literature review. She worked on the introduction (Section \ref{sec:intro}) with Catherine and literature survey (Section \ref{sec:survey}) of the paper. She helped finalize the slide-deck.

\paragraph{Mahesh Arumugam}
He worked on proof-of-concept implementation of \name. He designed the POC system and developed the story for the demo. Mahesh coded the FastAPI implementation of \ta. In addition, He helped write Section \ref{sec:method} (with Amrita) and Section \ref{sec:discussion} (with Geet). And, he helped typeset the paper in LaTeX.
